Memo of meeting

### 2018-07-13 paper/Chapters/Chapter2.tex
method updated 10%

\label{ChapterX} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}

@@

\section{Main Section 1}

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam ultricies lacinia euismod. Nam tempus risus in dolor rhoncus in interdum enim tincidunt. Donec vel nunc neque. In condimentum ullamcorper quam non consequat. Fusce sagittis tempor feugiat. Fusce magna erat, molestie eu convallis ut, tempus sed arcu. Quisque molestie, ante a tincidunt ullamcorper, sapien enim dignissim lacus, in semper nibh erat lobortis purus. Integer dapibus ligula ac risus convallis pellentesque.

%-----------------------------------
%	SUBSECTION 1
%-----------------------------------
\subsection{Subsection 1}

Nunc posuere quam at lectus tristique eu ultrices augue venenatis. Vestibulum ante ipsum primis in faucibus orci luctus et ultrices posuere cubilia Curae; Aliquam erat volutpat. Vivamus sodales tortor eget quam adipiscing in vulputate ante ullamcorper. Sed eros ante, lacinia et sollicitudin et, aliquam sit amet augue. In hac habitasse platea dictumst.

@@

\subsection{Subsection 2}
Morbi rutrum odio eget arcu adipiscing sodales. Aenean et purus a est pulvinar pellentesque. Cras in elit neque, quis varius elit. Phasellus fringilla, nibh eu tempus venenatis, dolor elit posuere quam, quis adipiscing urna leo nec orci. Sed nec nulla auctor odio aliquet consequat. Ut nec nulla in ante ullamcorper aliquam at sed dolor. Phasellus fermentum magna in augue gravida cursus. Cras sed pretium lorem. Pellentesque eget ornare odio. Proin accumsan, massa viverra cursus pharetra, ipsum nisi lobortis velit, a malesuada dolor lorem eu neque.

@@

\section{Main Section 2}

Sed ullamcorper quam eu nisl interdum at interdum enim egestas. Aliquam placerat justo sed lectus lobortis ut porta nisl porttitor. Vestibulum mi dolor, lacinia molestie gravida at, tempus vitae ligula. Donec eget quam sapien, in viverra eros. Donec pellentesque justo a massa fringilla non vestibulum metus vestibulum. Vestibulum in orci quis felis tempor lacinia. Vivamus ornare ultrices facilisis. Ut hendrerit volutpat vulputate. Morbi condimentum venenatis augue, id porta ipsum vulputate in. Curabitur luctus tempus justo. Vestibulum risus lectus, adipiscing nec condimentum quis, condimentum nec nisl. Aliquam dictum sagittis velit sed iaculis. Morbi tristique augue sit amet nulla pulvinar id facilisis ligula mollis. Nam elit libero, tincidunt ut aliquam at, molestie in quam. Aenean rhoncus vehicula hendrerit.

>>>>

\label{Chapter 2} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}

@@

\section{Strategy}

%-----------------------------------
%	SUBSECTION 1
%-----------------------------------
\subsection{Latent class analysis (LCA)}

@@

\subsection{Multilevel latent class analysis (MLCA)}

Multilevel latent class analysis accounts for the nested structure of the data by allowing latent class intercepts to vary across level 2 units and thereby examining if and how level 2 units influence the level 1 latent classes. These random intercepts allow the probability of
membership in a particular level 1 (observations) latent class to vary across level 2 units (e.g., here in the current context are the individuals). Essentially this allows the probability that an observation will belong to a
particular level 1 latent class to vary across Level 2 units (individuals).

\subsubsection{Parametric approach}

A traditional, parametric approach can be applied using a logistic regression model. In an unconditional logistic regression model, the probability of the outcome (i.e. being in latent class $k$) is constant within the 4-day survey for each individual (level 2). Therefore, say when we are fitting a model with $k (k = 1, \cdots, K)$ latent classes in level 1, then in each individual (level 2), there is a probability of being in latent class $k$. A random effect model consider the individual (level 2) to be drawn from a population of adults in the UK, and the probability of the outcome (i.e. being in latent class $k$) across individuals is considered to be a random variable \parencite{stawski2013multilevel}. The 2-level random intercept effect regression model can be expressed as:

\begin{equation}
\begin{aligned}
\text{logit}[P(C_{ij} = t)] & = \beta_{0j} & \textbf{(level 1)}  \\
\beta_{0j} & = \gamma_0 + \gamma_1 w_j + u_{0j} & \textbf{(level 2)} \\ 
\Rightarrow P(C_{ij} = t) & = \frac{\exp{(\gamma_0 + \gamma_1 w_j + u_{0j})}}{1 + \exp{(\gamma_0 + \gamma_1 w_j + u_{0j})}} \\
\end{aligned}
\end{equation}

Where we define:

\begin{itemize}
	\item $P(C_{ij} = t)$ as the probability that the observation is belonging to latent class $t$;
	\item $u_{0j}$ as the random intercept for $j$th individual; 
	\item the random intercept are assumed be normally distributed (i.e. $u_{0j} \sim N(0, \sigma_{u_0}^2)$), the magnitude of the $u_{0j}$ variance ($\sigma_{u_0}^2$) indicates the influence of the individuals (level 2);
	\item $w_j$ is the predictor for individual (level 2), such as age, and/or sex.
\end{itemize}

\begin{equation}
%\begin{aligned}
P(U_{ij1} = s_1, U_{ij2} = s_2, \cdots, U_{ijk} = s_{k}) = \sum_{t=1}^{T}P(C_{ij}=t)\prod_{k=1}^{K}P(U_{ijk} = s_k | C_{ij} = t)
%\end{aligned}
\label{MLCA}
\end{equation}

Where,

\begin{itemize}
	\item $ U_{ijk} $ represents the response of eating \textcolor{red}{high/low} carbohydrates on $i$th day of the survey ($i \in (1,2,3,4)$) in subject $j$ (level 2) at the $k$th hour of the day ($k \in (1, 2, 3, \cdots, 24)$);
	\item $C_{ij}$ denotes the latent class membership for subject $j$ on $i$th day of the survey;
	\item A specific latent class is referred to as $t$, and the total number of latent classes by $T$;
	\item $P(U_{ijk} = s_k|C_{ij} = t)$ is the probability of a specific response pattern, conditional on membership in latent class $t$.
\end{itemize}

The $P(C_{ij} = t)$ in equation \ref{MLCA} can be defined by following steps:

\subsubsection{Non-Parametric approach}

@@

\section{Survey Data}

%-----------------------------------
%	SUBSECTION 1
%-----------------------------------
\subsection{Survey Selection Method}

%-----------------------------------
%	SUBSECTION 2
%-----------------------------------
\subsection{Response rates}
